---
title: "Alzheimer's Analysis"
author: "Sneha Jacob, Alina Bangash, Jeremy Udo, Sana Akhtar, Jake Schwartz"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\newpage

# Introduction 
Our team decided to analyze the Alzheimer’s Disease dataset created by Rabei El Kharoua on Kaggle. We decided to proceed with this topic since Alzheimer’s is a very common illness without a cure that affects millions of people both directly and indirectly. This data set includes data from 2,149 patients and has 34 variables. Through this analysis we wanted to answer the question: Which factors are strongly associated with the diagnosis of Alzheimer's Disease? 

## Dataset Information:
- Age: age of patients (60-90 years)\
- Gender: 0 if male or 1 if female\
- Ethnicity: 0 - Caucasian, 1 - African American, 2 - Asian, 3 - other\
- Education Level: 0 - None, 1 - High School, 2 - Bachelors, 3 - Higher\
- BMI: Body Mass Index (15 - 40)\
- Smoking: 0 - No, 1 - Yes\
- Physical Activity: Weekly physical activity (0 - 10 hrs)\
- DietQuality: Diet quality score (0 -10)\
- SleepQuality: Sleep quality score (4 - 10)\
- Health History Variables (Categorical: 0 - No, 1 - Yes): 
    - FamilyHistoryAlzheimers
    - CardiovascularDisease
    - Diabetes
    - Depression 
    - HeadInjury
    - Hypertension\
- MMSE: Mini-Mental State Examination score (0 -30); lower score indicates cognitive impairment\
- FunctionalAsssessment: (0 -10); lower score indicates greater impairment\
- MemoryComplaints: 0 - No, 1- Yes\
- BehavioralProblems: 0 - No, 1 - Yes\
- ADL: Activities of Daily Living score, (0 -10); lower score indicates greater impairment\
- Symptom Variables (Categorical: 0 - No, 1 - Yes): 
    - Confusion
    - Disorientation
    - PersonalityChanges 
    - DifficultyCompletingTasks
    - Forgetfulness\
- Diagnosis: Diagnosis Status for Alzheimer’s Disease; 0 - No, 1 - Yes

# Neural Network:
We chose to start with a Neural Network to 

# Decision Tree:
## Model Formula: 
Our model formula for the decision tree is: \
*Diagnosis ~ PatientID + Age + Gender + Ethnicity + ... + DificultyCompletingTasks + Forgetfulness + Diagnosis + DoctorInCharge*

We decided to go forth with a decision tree since our response variable is qualitative. For the unpruned tree, we decided to use all thirty-five variables. Using this tree-based model allowed for an easier undestanding of which factors are associated with the diagnosis of Alzhiemer's Disease and through the classification tree, we can get a better understanding of which factors are most important through pruning. 

```{r}
library(tree)

```

# Conclusion: 




